Appendix 4: example of index standardization of fishery-independent survey data with inlabru

### 2021-12-13 doc/appendix-pcod-inlabru.Rmd
a little more inlabru organization

```{r mesh-sdmTMB, echo = TRUE, cache=FALSE}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)
```

@@

We can fit the model first with `sdmTMB`. Note that this is a model with only the fixed year effects and a single spatial field, with presence-absence as the response.

```{r}
sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year),
  data = pcod,
  time = "year", mesh = mesh,
  family = binomial(link = "logit"),
  spatiotemporal = "off",
  priors = sdmTMBpriors(
    matern_st = pc_matern(
      range_gt = 10, range_prob = 0.05,
      sigma_lt = 2, sigma_prob = 0.05
    )
  )
)
sdmtmb_coefs <- tidy(sdmtmb_fit, effects = "fixed")
```

@@

>>>>

@@

@@

We can also fit the model with `sdmTMB`. Note that this is a model with only the fixed year effects and a single spatial field, with presence-absence as the response.

```{r sdmtmb}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)

sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year),
  data = pcod,
  time = "year", mesh = mesh,
  family = binomial(link = "logit"),
  spatiotemporal = "off",
  priors = sdmTMBpriors(
    matern_st = pc_matern(
      range_gt = 10, range_prob = 0.05,
      sigma_lt = 2, sigma_prob = 0.05
    )
  )
)
sdmtmb_coefs <- tidy(sdmtmb_fit, effects = "fixed")
```
